Simulations log

### 2020-04-10 simulation_study/simulation/README.Rmd
update hyperopt, update meeting notes
Fix bug c parameter logistic config files

# transfer to harddrive 
transfer("hp", condition[8])
#sims[condition[8], , "one"] <- 3 # output is on harddrive
```

all - LCTD hyperparameters 
```{r}
# manually transform
# push to github 
sims[condition[4], , "all"] <- 1 # configs are on github 
```

>>>>

```{r}
sctd <- createLines(condition[3], d, "one")
write.table(sctd, file = "scripts/one/sctd.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(sctd) <- c("7945897", "7945899", "7945902", "7945903", "7945910", "7945912")
sims[condition[3], d, "one"] <- 2 # simulations are running

rcdd <- createLines(condition[7], d, "one")
write.table(rcdd, file = "scripts/one/rcdd.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(rctd) <- c("")
sims[condition[7], d, "one"] <- 2 # simulations are running

lcdd <- createLines(condition[8], d, "one")

10.04.2020

```{r}
# transfer to harddrive 
transfer("one", condition[8])
#sims[condition[8], , "one"] <- 3 # output is on harddrive
transfer("one", condition[4])

# simulations both failed? 
```

### all 
RCTD all
BCTD all 
LCTD all

```{r}
# manually transform
# push to github 
sims[condition[4], , "all"] <- 1 # configs are on github

```{r}
# run simulations 
lctd_n <- createLines(condition[4], d, "all")
write.table(lctd_n, file = "scripts/n/lctd_n.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
names(lctd_n) <- c()
#sims[condition[4], d, "all"] <- 2 # simulations are running

# transfer to harddrive 
transfer("n", condition[4])
#sims[condition[8], , "one"] <- 3 # output is on harddrive
```
